## Application

```{r}
library(tidyverse)
library(stringr)
train_labels <- read_csv("data/train.csv")
label_list <- strsplit(train_labels$tags, " ")
L <- unique(unlist(label_list))

Y <- ifelse(t(sapply(label_list, function(a) L %in% a)), 1, 0)
colnames(Y) <- L
Y <- data.frame(id = train_labels$image_name, Y, stringsAsFactors = FALSE)

library(mldr)

Y_mldr <- mldr_from_dataframe(Y, labelIndices = 2:18)
summary(Y_mldr)
```

+ small number of labels
+ cardinality quite similar to MULAN but small comparing to XML
+ density larger than most MULAN and probably a lot larger than XML
+ rel high IR - need to see CV of IR.
+ scumble: Our hypothesis is that the higher is the concurrence level the harder would be the work for resampling algorithms, and therefore the worse they would perform [@Charte]. Our scumble pretty average sized.

```{r}
Y_mldr$labels
```

```{r}
layout(matrix(c(1, 1, 6, 1, 1, 3, 5, 5, 3, 2, 4, 7), 4, 3, byrow = TRUE))
plot(Y_mldr, type = "LC")
plot(Y_mldr, type = "LH")
plot(Y_mldr, type = "LB")
plot(Y_mldr, type = "CH")
plot(Y_mldr, type = "LSB")
plot(Y_mldr, type = "AT")
plot(Y_mldr, type = "LSH")
```

+ actually seems pretty imbalanced from the plots - but don't think it is abnormal for ML.