# Introduction
\label{chp:intro}

## Motivation \label{sec:moti}

*Image Classification* is the task of assigning one (or more) label(s) to an input image. This seemingly simple task is one of the core problems in *computer vision*, and also has a large variety of practical applications. Examples of such applications include detecting deforestation in the Amazon from satellite images [^Amazon], or autonomous lung disease diagnosis from chest X-rays [@Wang2017]. Image classification is a thoroughly researched topic and already regarded by many to be a 'solved' problem. This progress is mainly attributed to the yearly large-scale image classification competition, called *ImageNet*[^imagenet], providing researchers with millions of labelled images to train their image classification models.

[^Amazon]: https://www.kaggle.com/c/planet-understanding-the-amazon-from-space
[^imagenet]: http://www.image-net.org/

The other driver of the recent success of image classification systems is the development of *Deep Learning* [@Lecun2015], a subfield of Machine Learning. Deep learning (by means of *deep neural networks*, or DNNs) extends upon artificial neural networks, which were designed in an attempt to mimic the structure and function of the human brain. The type of DNNs proven best suited for image classification problems is the class of *Convolutional Neural Networks* (CNNs). CNNs is the state-of-the-art model for practically all image classification problems. Its distinguishing feature from other methods is its ability to 'learn' highly discriminative feature representations of its input images, wheras the more conventional approaches require manually hand-crafting features for each specific task (as in SIFT [cite] and BoW [cite]). See \autoref{fig:ImNet} for an illustration of the impact CNNs made on image classification performance.

```{r, include=FALSE}
library(tidyverse)
p <- data.frame(Year = 2010:2017, Error = c(0.28191, 0.25770, 0.16422, 0.1174, 0.0666, 0.03567, 0.02991, 0.02251)) %>% 
  ggplot(aes(Year, Error)) + geom_line() + geom_point() + theme_minimal() +
  ggtitle("Error rate of winning ImageNet model by year") + 
  geom_hline(yintercept = 0.051, linetype = "dashed") + 
  scale_x_continuous(breaks = 2010:2017, minor_breaks = NULL) +
  scale_y_continuous(breaks = seq(0, 0.3, 0.05)) +
  annotate("text", x = 2012.1, y = 0.16422, label = "First CNN", hjust = 0) +
  annotate("text", x = 2010, y = 0.06, label = "Human performance", hjust = 0)

ggsave('figures/IN_perf.png', p, device = "png")
```

![Line graph illustrating the decreasing classification error rate of the winning ImageNet models by year\label{fig:ImNet}. Notice the large drop from 2011 to 2012 when the first CNN [@Krizhevsky2012] was used in this competition. Thereafter, all of the winning solutions made use of CNNs. CNNs are now able to surpass human level performace on this task.](figures/IN_perf.png)

Until recently, the main focus of deep learning approaches for image classification was on problems where each image is annotated with only a single label. *Multi-Label Classification* (MLC) [@Zhang2014] of images generalises this task to allow images to be simultaneously annotated with more than one label. The number of labels to associate with each image, is unknown, and differs across images. Clearly by definition, multi-label image classification is much more challenging than conventional (single-label) classification. Moreover, since the majority of real-world images contain more than one object, multi-label image classification is a more generally occurring problem in practice than single-label classification. In research, it was only fairly recently that more attention was paid to multi-label image classification (for example in [@Wei2014]). Therefore the field is regarded far from the maturity level of its single-label counterpart. Since DNNs have proven to be so successful in the case of single-label image classification, it seems reasonable to ask whether their use may not also be extended to successfully annotate images with multiple labels.

Extending CNNs and other DNNs to handle images with multiple labels is not a trivial task. Thus far only a handful of proposals regarding how to tackle multi-label image classification have been published (for example in [@Gong2013], [@Wei2014], [@Wang2016], [@Zhu2017], [@Chen2017], more?). These contributions were however mostly made in isolation of one another – hence no comprehensive comparison of these methods (whether theoretical or empirical) can be found. Also, the majority of proposals stem from a deep learning background and could possibly gain from insights and methods already discovered in the MLC field.

In summary, the relevance of multi-label image classification in terms of its wide range of useful practical applications, combined with the power of deep learning methods for image classification tasks, forms the main motivation for the chosen research topic. Deep learning for multi-label image classification constitutes a research area that seems still to be relatively under-explored. As such, it may well be that a comprehensive understanding and review of the subject could lead to novel contributions. 

## Objectives \label{sec:obj}

The core objective of this study is to learn how to effectively apply DNNs in a multi-label image classification context. In its pursuit, a thorough understanding of the following research areas seems essential:

+ **The image classification problem** - Since this is the application domain of the envisioned research, a good understanding of the problem forms a solid foundation for further study in the domain. Through a discussion of current approaches to the problem, challenges and possible shortcomings in multi-label image classification may be identified.

+ **Deep neural networks** - Being the class of algorithms which the study focuses on, an understanding of DNNs is essential to further explore ways in which to extend this class of models. Attention should be paid to the typical structures of DNNs in the context of image classification. Another important aspect is the way in which variations in DNN architectures influence the effectiveness of algorithms in scenarios of interest. Moreover, learning about the limitations of current networks may aid in directing the study.

+ **The multi-label classification framework** - This is the *supervised learning* paradigm within which the research takes place. Although many contributions have been made to the MLC field, most MLC procedures only recently became more popular. Knowledge of the underlying concepts (especially those that may be considered novel relative to single-label classification), and insight into state-of-the art algorithms and challenges in the field, should guide the research. Although the focus will mainly be guided by the application domain, a review of previous work on multi-label image classification (other than DNNs) may also prove insightful.

The above objectives regarding the literature review are of course complementary to the main objective of the study, which may be partitioned as follows: 

+ **Extensions of DNNs to the MLC problem domain ** - Despite sparse literature contributions in this regard, there exists a sufficient body of proposals in order to warrant a review on the subject. The aim will be to obtain a thorough understanding of each proposal in terms of both the way in which it solves the MLC problem, and in terms of its effectiveness in doing so. Conceptual differences among the approaches should form an important focus. If proposals for DNNs in MLC with other application domains are found, the possibility of transferring them to image classification should also be considered.

+ **Improvements to existing approaches** - Learning from the strengths and weaknesses of each existing approach should provide a good basis for further research in terms of either extensions of existing approaches, or in terms of entirely novel proposals. The possibility of transferring ideas in pure MLC to deep learning to improve upon existing approaches should also be explored.

+ **Empirical evaluation and comparison of approaches** - The literature review and theoretical comparisons should be complemented by empirical evaluations. Existing and proposed classification procedures may be evaluated and compared by means of benchmark image datasets. The practical implementation of algorithms may highlight challenges that may not necessarily be found in the literature. 

Through the above objectives, the thesis should guide a reader to a thorough understanding of recent work on DNNs for multi-label image classification. Given a certain multi-label image classification problem, one should be able to recommend some approaches above others, know their advantages and limitations, and effectively implement them.

## Contributions

> rough - will complete after the contributions are actually done. This is roughly what I attempt to contribute.

> should go at the end

Novel contributions made to the literature by this thesis:

+ First review of multi-label DNNs - there are a few papers on ML-CNN. They are usually compared to only a limited number of other approaches, on limited number of datasets and limited number of metrics. To the best of our knowledge, at the time of completing this thesis, no other work provides such an extensive review of the literature.

+ Some of the proposed algorithms empirical evaluations are lacking completeness. Usually they lack combinations of either or all of the following:

    + evaluated on multiple benchmark datasets
    + evaluated in terms of a representative set of multi-label evaluation metrics
    + estimated errors provided with standard errors
    + compared with a wide range of state-of-the-art algortihms

+ improvements on existing approaches?

## Code and Reproducibility

All of the code for this project, including the source docoments, is made available in the Thesis Github repository [^repo]. More instructions on how to implement the code is contained in the file named, `README.md`, in the repository.

> not sure about this section

> too short. Where should I rather mention this?

[^repo]: https://github.com/jandremarais/Thesis

## Background and Important Concepts

In this thesis, the three key topics of this study, *viz*. image classification, deep neural networks and multi-label classification, will be introduced in their own chapters (image classification here, and the other in the following two chapters). Thereafter, a discussion of the combination of the above topics, in order to conceptualise image classification by means of DNNs for MLC, will follow.

Since we are interested in applying DNNs for MLC in the image classification domain, some background on image classification is first required. Image classification is an example of a *superivised learning* task, hence in the remainder of this chapter, we start with a brief introduction to supervised learning followed by the general problem of image classification. Discussions of DNNs and of MLC follow in Chapters \ref{chp:dnn} and \ref{chp:mlc} respectively. A more comprehensive outline of the thesis may be found in \Cref{sec:outline}.

### Statistical Learning \label{sec:Slearning}

Machine or statistical (used interchangably) learning algorithms are used to perform certain task that are too difficult or inefficient to solve with fixed rule-based programs. These algorithms are able to learn how to perform a task from data. For an algorithm to learn from data means that it can improve its ability in performing an assigned *task*, with respect to some *performance measure*, by processing the *data*. This section gives a brief look at some of the important types of tasks, data and performance measures in the field of statistical learning.

A learning task describes the way an algorithm should process an observation. An observation is a collection of features that have been measured from some object or event that we want the system to process, like an image. We will represent an observation by a vector $\boldsymbol{x}\in\mathbb{R}^{p}$ where each element $x_{j}$ of the vector is an observed value of the $j$-th feature, $j=1,\dots,p$. For example, the features of an image are usually the color intensity values of the pixels in the image.

Many kinds of tasks can be solved with statistical learning. One of the most common learning tasks is that of *classification*, where it is expected of an algorithm to determine which of $K$ categories an input belongs to. To solve the classification task, the learning algorithm is usually asked to produce a function $f:\mathbb{R}^{p}\to \{1,\dots,K\}$. When $y=f(\boldsymbol{x})$, the model assigns an input described by the vector $\boldsymbol{x}$ to a category identified by the numeric code $y$, called the output or response. In other variants of the classification task, $f$ may output a probability distribution over the possible classes.

*Regression* is the other main learning task and requires the algorithm to predict a continuous value given some input. This task requires a function $f:\mathbb{R}^{p}\to\mathbb{R}$, where the only difference to classification is the format of its output.

Learning algorithms can learn to perform such tasks by observing a relevant set of data points, *i.e.* a dataset. A dataset containing $N$ observations of $p$ features is commonly described as a design matrix $X:N\times p$, where each row of the matrix represents a different observation and each column corresponding to a different feature of the observations, *i.e.*

$$
X = 
\begin{bmatrix}
x_{11} & x_{12} & \dots & x_{1p}\\
x_{21} & x_{22} & \dots & x_{2p}\\
\vdots & \vdots & \ddots & \vdots\\
x_{N1} & x_{N2} & \dots & x_{Np}
\end{bmatrix}.
$$
Often the dataset includes annotations for each observation in the form of a label (classification) or a target value (regression). The $N$ annotations are represented by the vector $\boldsymbol{y}$, where element $y_{i}$ is associated with the $i$-th row of $X$.

$$
\boldsymbol{y}=
\begin{bmatrix}
y_{1}\\
y_{2}\\
\vdots\\
y_{N}
\end{bmatrix}.
$$
Note, in the case of multiple labels or targets, a matrix representation $Y:N\times K$ is required.

Statistical learning algorithms can roughly be divided into two main categories, *supervised* and *unsupervised* algorithms, determined by the presence of annotations in the dataset to be analysed. Unsupervised learning algorithms learn from data consisting of only features, $X$, and are used to find useful properties and structure in the dataset [see @Hastie2009, Ch. 14]. On the other hand, superivised learning algorithms learn from datasets which consist of both features and annotations, $(X,Y)$, with the aim to model the relationship between them. Therefore, both classification and regression are considered supervised learning tasks.

In order to evaluate the ability of a learning algorithm to perform its assigned task, we must design a quantitative measure of its performance. For example, in a classification task we are usually interested in the accuracy of the algorithm, *i.e.* the percentage of times the algorithm makes the correct classification. We are mostly interested in how well the learning algorithm performs on data that it has not seen before, since this demonstrates how it will work in real-world situations. Thus we evaluate the algorithm on a *test set* of data points, alternative to the *training set* of data points used in the learning process.

Consider the following example of a simple learning algorithm, known as *linear regression*, to give a more concrete understanding of supervised learning. The goal here is to build a system that can take a vector $\boldsymbol{x}\in \mathbb{R}^{p}$ as input and predict the value of a scalar $y\in \mathbb{R}$ as its output. In the case of linear regression we assume the output be a linear function of the input. Let $\hat{y}$ be the predicted value of $y$. We define the output to be 

$$
\hat{y}=\hat{\boldsymbol{w}}^{T}\boldsymbol{x},
$$
where $\hat{\boldsymbol{w}}=[w_{0},w_{1},\dots,w_{p}]$ is a vector of paramaters and $\boldsymbol{x}=[1,x_{1},x_{2},\dots,x_{p}]$ to include the intercept in the model (also known as the *bias* in machine learning, not to be confused with bias in the statistical sence). The paramaters are values that control the behaviour of the system. We can think of them as a set of *weights* that determine how each feature affects the prediction. So the learning task can be defined as: to predict $y$ from from $\boldsymbol{x}$ by outputting $\hat{y}=\hat{\boldsymbol{w}}^{T}\boldsymbol{x}$. Keep in mind for now that the linear model is one of the main building blocks of neural networks.

Next, we need a defintion of a performance measure to evaluate the predictions made by the algorithm. The evaluation metric tells us how (dis)similar the predicted output is to the actual response values for a set of observations. A very common measure of performance in regression is the *mean squared error* (MSE) of the model, given by:

$$
MSE = \frac{1}{N}\sum_{i=1}^{N}(y_{i}-\hat{y}_{i})^{2},
$$
evaluated on a set of $N$ observations. The process of learning from the data (or fitting the model to the data) can be reduced to the optimisation problem of finding the set of weights, $\hat{\boldsymbol{w}}$, producing a $\hat{\boldsymbol{y}}$ that minimises the MSE. This problem has a closed form solution and can quite trivially be found by means of *ordinary least squares* (OLS) [see @Hastie2009, p. 12]. However, we have mentioned that we are actually more interested in the algorithm's performance evaluated on a test set. Unfortanately, the least squares solution does not guarrantee the optimal solution in terms of the MSE on a test set, making statisitical learning more than a pure optimisation problem.

The ability of a model to perform well on previously unobserved inputs is referred to as its *generalisation* abiltiy. Generalisation is the central challenge of statistical learning. One way of improving the generalisation ability of a linear regression model is by modifying the optimisation criterion $J$, to include a *weight decay* (*aka.* *regularisation*) term:

$$
J(\boldsymbol{w})=MSE_{\text{train}} +\lambda\boldsymbol{w}^{T}\boldsymbol{w}
$$
Since we want to minimise $J$, the optimisation criterion now expresses preference for sets of weights with smaller values. $\lambda$ is a non-negative value chosen ahead of time. It controls the strength of the preference by determining how much influence the penalty term, $\boldsymbol{w}^{T}\boldsymbol{w}$, has on the optimisation criterion. If $\lambda=0$, no preference is imposed and the solution is equivalent to the OLS solution. Larger values of $\lambda$ forces the weights to become smaller, hence also known as a shrinkage method ([see @Hastie2009, pp. 61-79] for more on such methods and why they work). This approach of modifying the learning algorithm to attempt to reduce its generalisation error is known as *regularisation* [@Goodfellow2016, pp. 118-120].

We can further generalise linear regression to the classification scenario. First, note the different types of classification schemes. Consider $\mathcal{G}$, the discrete set of values which may be assumed by $G$, where $G$ is used here to denote a categorical output variable (instead of $Y$). Let $|\mathcal{G}|=K$ denote the number of discrete categories in the set $\mathcal{G}$. The simplest form of classification is known as binary classification and refers to scenarios where the input is associated with only 1 of possible 2 classes, *i.e.* $K=2$. When $K>2$, the task is known as multiclass classification. In multi-label classification an input may be associated with more than one of a possible $K$ classes, where the number of classes each observation belongs to is unknown. A thorough discussion of MLC methods are given in \Cref{chp:mlc}. Here, we will consider the single label cases of binary and multiclass classification.

In multiclass classification, given the input values $\boldsymbol{X}$, we would like to make good predictions of the output, $G$, which we denote as $\hat{G}$. One approach would be to denote $G$ as an indicator vector $\boldsymbol{Y}$, where its elements are all zero except at the $G$-th position where it is coded as a 1, *i.e.* $Y_{k}=1$ for $k=G$ and $Y_{k}=0$ for $k\neq G$. Then we can treat each of the elements in $\boldsymbol{Y}$ as quantitative outputs and predict values for it denoted by $\hat{\boldsymbol{Y}}=[\hat{Y}_{1},\dots,\hat{Y}_{K}]$. The class with the highest predicted value is then the final categorical output, *i.e.* $\hat{G}=\arg\max_{k\in\{1,\dots,K\}}\hat{Y}_{k}$.

Thus we seek a function of the inputs that can produce predictions of the class scores, *i.e.*

$$
\hat{Y}_{k}=\hat{f}_{k}(\boldsymbol{X}),
$$
for $k=1,\dots, K$, where $\hat{f}_{k}$ is an estimate of the true function, $f_{k}$ representing the relationship between the inputs and the outputs of class $k$. As with the linear regression case described above, we can use a linear model $\hat{f}_{k}(\boldsymbol{X})=\hat{\boldsymbol{w}}_{k}^{T}\boldsymbol{X}$ to approximate the true function. The linear model for classification divides the input space into a collection of regions labelled according to the classification, where the division is done by linear *decision boundaries* (see \autoref{fig:sgd} for an illustration). The decision boundary between classes $k$ and $l$ is the set of points for which $\hat{f}_{k}(\boldsymbol{x})=\hat{f}_{l}(\boldsymbol{x})$. These set of points form an affine set or hyperplane in the input space.

After the weights are estimated from the data, an observation represented by $\boldsymbol{x}$ (including the unit element) can be classified as follows:

+ compute $\hat{f}_{k}(\boldsymbol{x})=\hat{\boldsymbol{w}}_{k}^{T}\boldsymbol{x}$ for all $k=1,\dots,K$
+ identify the largest component and classify accordingly, *i.e.* $\hat{G}=\arg\max_{k\in\{1,\dots,K\}}\hat{f}_{k}(\boldsymbol{x})$

One may view the predicted class scores as estimates of the conditional class probabilities (or posterior probabilities), *i.e.* $P(G=k|\boldsymbol{X}=\boldsymbol{x})\approx \hat{f}_{k}(\boldsymbol{x})$. However, these values are not the best estimates of posterior probabilities. Although the values sum to 1, they do not lie within [0,1]. A way to overcome this problem is to estimate the posterior probabilities
using the *logit transform* of $\hat{f}_{k}(\boldsymbol{x})$. That is,

$$
P(G=k|\boldsymbol{X}=\boldsymbol{x})\approx\frac{e^{\hat{f}_{k}(\boldsymbol{x})}}{\sum_{l=1}e^{\hat{f}_{l}(\boldsymbol{x})}}.
$$
Through this transformation, the estimates of the posterior probabilities both sum to 1 and are squeezed into [0,1]. The above model the well-known *logistic regression* model [@Hastie2009, p. 119]. With this formulation there is no closed form solution for the weights. Instead, the weight estimates may be searched for by maxmising log-likelihood. One way of doing this is by minimising the negative log-likelihood using gradient descent, which will be discussed in the following section.

Finally, note that supervised learning problem problem can also be viewed as a function approximation problem. Suppose we are trying to predict a variable $Y$ given an input vector $\boldsymbol{X}$ where we assume the true relationship between them is given by:
$$
Y=f(\boldsymbol{X})+\epsilon,
$$
where $\epsilon$ stands for the part of $Y$ that is not predictable from $\boldsymbol{X}$, because of, for example, incomplete features or noise present in the labels. Then in function approximation we are estimating $f$ with an estimate $\hat{f}$. In some cases, like in the linear regression example, the estimation of $f(\boldsymbol{X},\theta)$ is equivalent to estimating the optimal set of weights, $\hat{\theta}$. For the remainder of the thesis, we refer to $\hat{f}$ as the *model*, *classifier* or *learner*.

### Optimisation \label{sec:optimisation}

We mentioned that the fitting of a linear regression model can be reduced to finding the optimal weights to minimise the MSE function (with or without weight decay). Similarly, most (all?) model training procedures can be described as the search for its internal paramaters that minimises/maximises some *objective function*. Therefore, statistical learning and optimisation are closely related. Optimisation refers to the task of either minimising or maximising some function $J(x)$ by altering $x$. Although, we usually phrase most optimisation problems in terms of minimisation. The function we want to optimise is called the objective function. When we are minimising the objective function, we may also refer to it as the *cost* or *loss function*. These terms will be used interchangeably throughout the remainder of the thesis.

As mentioned in the previous section, parameter estimation (or optimisation) of a linear (or logistic regression) model is usually done using OLS or maximum likelihood estimation (MLE). In this section, however, we discuss an alternative parameter estimation method also relevant for optimisation of neural networks.

Consider the MSE loss function:

$$
\begin{aligned}
L&=\sum_{i=1}^{N}L_{i}\\
&=\sum_{i=1}^{N}\sum_{k=1}^{K}(y_{ik}-f_{k}(\boldsymbol{x}_{i}))^{2}\\
&=\sum_{i=1}^{N}\sum_{k=1}^{K}(y_{ik}-\boldsymbol{w}_{k}^{T}\boldsymbol{x}_{i})^{2},
\end{aligned}
$$
where $f_{k}(\cdot)$ in this case is the linear model used to predict the $k$-th class posterior probability. Although the MSE loss is mostly used in a regression setup and not really well suited for classification, we make use of it here for illustration purposes.

To find the weights, $\boldsymbol{w}$, that minimise $L$, we can follow a process of iterative refinement. That is, starting with a random initialisation of $\boldsymbol{w}$, one iteratively updates the values such that $L$ decreases. The updating steps are repeated untill the loss converges. In order to minimise $L$ with respect to $\boldsymbol{w}$ we calculate the gradient of the loss function at the point, $L(\boldsymbol{x};\boldsymbol{w})$. The gradient (or slope) of the loss function tells us the direction in which the function has the steepest rate of increase. Therefore, once we determined this direction, we can update the weights by a step in the opposite direction - thereby reaching a smaller value of $L$.

The gradient of $L_{i}$ is computed by taking the partial derivative of $L_{i}$ in terms of $\boldsymbol{w}_{k}$, *i.e.*:

$$
\frac{\partial L_{i}}{\partial\boldsymbol{w_{k}}}=-2(y_{ik}-\boldsymbol{w}_{k}^{T}\boldsymbol{x}_{i})\boldsymbol{x}_{i}
$$
Given the above derivatives, an update at the $(r+1)$-th iteration has the form

$$
\boldsymbol{w}_{k}^{(r+1)}=\boldsymbol{w}_{k}^{(r)}-\gamma\sum_{i=1}^{n}\frac{\partial L_{i}}{\partial\boldsymbol{w_{k}^{(r)}}},
$$
where $\gamma$ is called the *learning rate* and determines the size of the step taken into the optimal direction. One typically wants to set the learning rate small enough so that the step does not overshoot the minimum, but big enough to limit the number of iterations before convergence. This value can be determined via a line search but is not always ideal since the training time of DNNs are too long. Another option is to reduce the learning rate after every fixed number of iterations, but more detail regarding the implication of the learning rate will be given in \Cref{chp:DNN}.

This procedure of repeatedly evaluating the gradient and then performing a parameter update is called *gradient descent* [Cauchy, 1847]. Gradient descent forms the basis of the optimisation procedure for neural networks.

Notice that a weight update is made by evaluating the gradient over a set of observations, $\{\boldsymbol{x}_{i},i=1,\dots,n\}$. One of the advantages of gradient descent is that at an iteration, the gradient need not be computed over the complete training dataset, *i.e.* $n\le N$. When updates are iteratively determined by using subsets of the data, the process is called *mini-batch gradient descent*. This is extremely helpful in large-scale applications, since since it obviates computation of the full loss function over the entire dataset. This leads to faster convergence, because of more frequent parameter updates, and allows for the processing of large datasets that are too big to fit into a computer's memory. The choice in batch size depends on the available computation power, but typically a batch consists of 64, 128 or 256 data points, since in practice many vectorised operation implementations work faster when their inputs are sized in powers of 2. The gradient obtained using mini-batches is only an approximation of the gradient of the full loss but it seems to be sufficient in practice [@Li2014]. Note at this point that the collection of iterations needed to make one sweep through the training set is called an *epoch*.

The extreme case of mini-batch gradient descent is when the batch size is selected to be 1. This is called *Stochastic Gradient Descent* (SGD). Recently SGD has been used much less, since it is more efficient to calculate the gradient in larger batches compared to only using one example. However, note that it remains common to use the term SGD when actually referring to mini-batch gradient descent. Gradient descent in general has often been regarded as slow or unreliable but it works well for optimising DNNs. SGD will most probably not find even a local minimum of the objective function, it usually however find a very low value of the cost function quickly enoguh to be useful.

### Optimisation Example

To illustrate the SGD algorithm, consider the linear model in a classification context. Suppose we are given a training set with 2-dimensional inputs with only two possible classes. Let the data be generated in the same manner as described in [@Hastie2009, pp. 16-17]. We want to fit a linear regression model to the data such that we can classify an observation to the class with the highest predicted score. In the binary case it is only necessary to model one class probability and then assign an observation to that class if the score exceeds some threshold (usually 0.5), otherwise it is assigned to the other class. Therefore the decision boundary is given by $\{\boldsymbol{x}:\boldsymbol{x}^{T}\hat{\boldsymbol{w}}=0.5\}$.

The example is illustrated in \autoref{fig:sgd}. The colour shaded regions represent the parts of the input space classified to the respective classes determined by the decision boundary with the OLS parameter estimates. Gradient descent was applied to the determine the optimal weights using a learning rate of 0.001. Since the total number of training observations are small, it is not necessary to use SGD. In \autoref{fig:sgd} the dashed lines represent the decision boundary defined by the gradient descent paramater estimates at different iterations. We observe that initially the estimated decision boundary is far from the OLS solution, but as the update iterations are continued, the decision boundary is rotated and translated until finally matching the OLS line. It took 29 iterations for the procedure to reach convergence.

```{r, cache=TRUE, fig.cap = "Plots of gradient descent example. (a) The data points plot in the input space. The shade in the background represents the class division in the input space with the decision boundary determined by linear least squares estimation. The dashed lines represent the decision boundaries learned at different iterations. (b) The loss calculated at each iteration. \\label{fig:sgd}"}
# generate the data
set.seed(1)

K <- 2
m <- lapply(list(c(1, 0), c(0, 1), c(3, 3))[1:K], 
            function(a) mvrnorm(n = 10, mu = a, Sigma = diag(2)))

X <- lapply(m, function(b) {
  t(sapply(1:100, function(a) {
    mvrnorm(n = 1, mu = b[sample(10, 1), ], Sigma = diag(2)/5)
  }))
})

D <- data.frame(X = do.call("rbind", X), Y = rep(0:(K-1), each = 100))
D <- cbind(X.0 = 1, D)
#D[, -3] <- scale(D[, -3])

# SGD
lin_model <- function(x, b) sum(x * b)
L <- function(y, yhat) sum((y - yhat)^2)

set.seed(125)
B <- mvrnorm(1, mu = c(0, 0, 0), Sigma = diag(3))
B_mat <- B
yhat <- apply(D[, -3], 1, function(a) lin_model(a, B))
loss <- L(D$Y, yhat)
lr <- 0.001
for(i in 1:200) {
  gradient <- c(-2*t(as.matrix(D[, -4])) %*% (D$Y - yhat))
  B_new <- B - lr * gradient
  
  yhat <- apply(D[, -4], 1, function(a) lin_model(a, B_new))
  loss <- c(loss, L(D$Y, yhat))
  
  if(abs(loss[i+1] - loss[i]) < 0.00001) {
    return()
  } else {
    B <- B_new
    B_mat <- rbind(B_mat, B_new)
  }
  #B <- B_new
}

x <- as.matrix(D[, -4])
Bhat <- solve(t(x)%*%x)%*%t(x)%*%D$Y

d_bounds <- t(apply(B_mat, 1, function(a) c(slope = -a[2]/a[3], intercept = (0.5-a[1])/a[3])))
rownames(d_bounds) <- NULL
d_bounds <- data.frame(iteration = 0:(nrow(d_bounds)-1), d_bounds)
d_bounds <- d_bounds[c(1, 5, 10, 30), ]

xlims <- range(D$X.1) * 1.1
ylims <- range(D$X.2) * 1.1

shade_x <- seq(xlims[1], xlims[2], len = 100)
shade_y <- -shade_x*Bhat[2]/Bhat[3] + (0.5 - Bhat[1])/Bhat[3]
shade_y[shade_y>ylims[2]] <- ylims[2]

db_coords <- t(sapply(1:nrow(d_bounds), function(a) {
  ycut <- xlims[2] * d_bounds[a, "slope"] + d_bounds[a, "intercept"]
  if(ycut < ylims[2]) {
    c(xlims[2], ycut)
  } else {
    c((ylims[2] - d_bounds[a, "intercept"])/ d_bounds[a, "slope"], ylims[2])
  }
}))
colnames(db_coords) <- c("dx", "dy")
d_bounds <- cbind(d_bounds, db_coords)

library(latex2exp)
# Plot
p <- D %>% 
  ggplot() + 
  geom_point(aes(X.1, X.2, color = factor(Y)), show.legend = FALSE)+
  #coord_fixed() +
  theme(panel.background = element_rect(fill = "white")) +
  geom_abline(data = d_bounds, aes(slope = slope, intercept = intercept), linetype = "dashed") +
  geom_ribbon(data = data.frame(shade_x, shade_y),
            aes(x = shade_x, ymin = ylims[1], ymax = shade_y), alpha = 0.15, fill = "red") +
  geom_ribbon(data = data.frame(shade_x, shade_y),
            aes(x = shade_x, ymin = shade_y, ymax = ylims[2]), alpha = 0.15, fill = "blue") +
  scale_y_continuous(expand = c(0, 0), name = TeX("$X_2$"), breaks = NULL) + 
  scale_x_continuous(expand = c(0, 0), name = TeX("$X_1$"), breaks = NULL) +
  geom_text(data = d_bounds, aes(dx, dy, label = paste0("i=", iteration)), hjust = c(1, rep(0, 3)), 
            vjust = c(0, rep(1, 3)), nudge_y = c(0, rep(-0.02, 3)), nudge_x = c(-0.02, rep(0, 3))) +
  panel_border(colour = "black")

loss_data <- data.frame(loss = loss, iteration = 0:(length(loss) - 1)) 
library(ggthemes)
p_loss <- loss_data %>% 
  ggplot(aes(iteration, loss)) + 
  geom_line(color = "blue") +
  theme(axis.ticks.y = element_blank()) +
  # theme(panel.background = element_rect(fill = "white"),
  #       axis.ticks.x = element_blank()) +
  geom_segment(data = loss_data[c(1,5,10,30), ], aes(x = iteration, xend = iteration, yend = 0), linetype = "dashed") +
  scale_y_continuous(expand = c(0, 0), labels = NULL) + 
  scale_x_continuous(expand = c(0.05, 0), breaks = c(0, 4, 9, 29))

plot_grid(p, p_loss, labels = c("(a)", "(b)"), nrow = 1, align = "vh", rel_widths = c(3,2))
```

Since deep learning is a specific kind of statistical learning, it can also be decomposed into the same components of: model, loss funciton, optimisation prodcedure and dataset. We have discussed all of these ingredients in simple and general terms, and are now ready to narrow the focus to deep learning methods. The next section on image classification introduces the type of data we will be using for this research.

### Image Classification

We have already introduced the statistical learning task of classification. As can be derived by its name, image classification refers to this task but narrowed down to the case where the inputs are images, *i.e* the task is to assign labels to images. Just like in the general classification case, the main focus up until recently was restricted to images associated with a single label. The more general case, and the focus of this thesis, where images can belong to more than one class simultaneously (for example images containing more than one object) is still relatively new. For this section we will mostly consider the single-label classification case, but most of the concepts are transferable to multi-label image classification. The novel concepts and challenges of multi-label image classification will be introduced in \Cref{chp:mlc} and \Cref{chp:DNN-MLC}.

Before the age of deep learning, the main point of consideration for image classification was how to numerically represent images in such a way that an image classifier can distinguish between its classes, *i.e.* what features to extract from the images to be used as input. Before answering this question we need a better understanging of the nature of images as inputs and how they can represented in a digital format.

An image is made up of a grid of many tiny square cells of different colors. These cells are known as pixels and one pixel represents one color. A grayscale image, 32 pixels wide and 32 pixels long, can be represented by a $32\times 32$ matrix of integers, where each integer represents the 'brightness' (intensity) of each pixel. These integers are usually in $[0,255]$, such that the greater the integer the brighter the pixel, *i.e.* a pixel with intensity 0 is totally black and a pixel with intensity 255 is totally white. \autoref{fig:img_mat} illustrates this representation. Note, that a standard color image consists of 3 spectral bands, red, green and blue (RGB), *i.e.* the color of one pixel is determined by 3 integers in $[0,255]$, each representing the intensity of the color red, green and blue, respectively. Thus a $32\times32$ sized image is represented by an array of size $32\times32\times3$.

```{r,fig.cap="A low resolution grayscale profile of a man with pixel values overlayed on the image.\\label{fig:img_mat}", cache=TRUE, fig.width=3, fig.height=3}
load.image("figures/wim.jpeg") %>% 
  grayscale %>% 
  resize(16, 16) %>% 
  as.data.frame %>% 
  ggplot(aes(x, y)) + 
  geom_raster(aes(fill = value), show.legend = FALSE) +
  scale_y_continuous(trans=scales::reverse_trans(), expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0)) + 
  scale_fill_gradient(low = "black", high = "white") +
  coord_fixed() +
  theme(text = element_blank(), line = element_blank()) +
  geom_text(aes(label = round(value * 256), color = value), show.legend = FALSE, size = 2) +
  scale_color_gradient(low = "white", high = "black")
```

A straighforward approach to transforming an array of pixel intensities to a representation fitting the input format of conventional classifiers is to *flatten* each array into a vector of size $width \times height \times channels$. For example a hypothetical grayscale image of size $3\times 3\times1$ is transformed as:

$$
\begin{bmatrix}
x_{1} & x_{2} & x_{3}\\
x_{4} & x_{5} & x_{6}\\
x_{7} & x_{8} & x_{9}
\end{bmatrix}
\to
\begin{bmatrix}
x_{1} & x_{2} & x_{3} &x_{4} & x_{5} & x_{6} & x_{7} & x_{8} & x_{9}
\end{bmatrix}.
$$

Needless to say, this representation is not very effective. Firstly, this transformation discards most of the shape and structural information of an image. In addition, these flattened vectors are very high-dimensional ($p = 256\times 256 \times 3 = 196608$ for a colour image of size $256\times 256$), subjecting the classifier to the well-known problem in statistical learning, the *curse of dimensionality* [@Hastie2009, pp. 22-27].

On top of that, in a typical image classification, the images in its raw representation can have high intra-class variance and/or very low inter-class variance - making it extremely difficult for even the state-of-the-art classifiers, such as Random Forests, Support Vector Machines and Boosting to discriminate between classes. The intra-class variation can come from different viewpoints, scales, illumination and backgrounds of images of the same object, amongst others (see \autoref{fig:intra-inter}). On the other hand, suppose the task is to distinguish between an ostrich and an emu from an image. Then there will be very little variation between the classes (inter-class) since the two species look very similar.

```{r, echo=FALSE, cache=TRUE, fig.cap="ImageNet examples of ostriches (a) and emus (b) showing the intra-class and inter-class variations. Notice how different images of are of the same class but also how similar they are between classes\\label{fig:intra-inter}."}
library(png)
library(grid)
library(gridExtra)
library(cowplot)
library(tidyverse)

plot_png <- function(fname, interpolated = TRUE){

  img <- readPNG(fname) %>%
    rasterGrob(interpolate = interpolated)# enable/disable linear interpolation
  ggplot() +
    annotation_custom(img,
                      xmin = -Inf,
                      xmax = Inf,
                      ymin = -Inf,
                      ymax = Inf)

}

img1 <- plot_png("figures/ostrich2.png")
img2 <- plot_png("figures/emu.png")
#grid.arrange(img1, img2, ncol = 2)

plot_grid(img1, img2, labels = c('(a)', '(b)'), vjust = 2.5)
```

To compensate for this problem one can attempt to extract features from images for which the intra-class variation is lower and the inter-class variance higher. Before we had the computational power to optimise DNNs this was the standard procedure in image classification - designing feature representation of images that are much easier for conventional classifiers to learn from than raw pixel data. Building these feature representations can become quite complex. The most popular representation (before deep learning) for classification is the Bag-of-Visual words (BoV) [@Csurka2004]. Without going into too much detail, the BoV approach consists of extracting a set of local descriptors of images (see *Scale Invariant Feature Transform* (SIFT) [@Lowe2004] and *Histogram of Oriented Gradients* (HOG) [@Dalal2005]), encoding them into a high-dimensional vector (see *Fisher Vectors* [@Sanchez2013]) and then pooling them into an image level signature (see *Spatial Pyramid Pooling* [@Lazebnik2006]).

As mentioned before, this approach to image classification is not trivial, with many complex facets to the modelling process. It usually requires considerable engineering skill and/or domain expertise. In addition, these feature representations are only suited for a narrow subset of image classification tasks and do not generalise well. This is where deep learning methods prove to be superior, since it has the ability to learn these feature representations from the data. This is discussed in detail in the next chapter. Hopefully now the reader has a better understanding of the image classification problem in general, which will most likely lead to a better appreciation of the power and effectiveness of deep learning methods.

## Outline \label{sec:outline}

From this point on the reader should have a basic understanding of the topic of this thesis. The reasons why this topic was chosen has been described in \Cref{sec:moti} section and the goals of completing this thesis under the \Cref{sec:obj}. The problem of image classification has been introduced with the help of basic examples, along with a brief conceptual description of the multi-label image classification problem. Therefore, the reader should also be comfortable with the problem we want the DNNs to solve and the common challenges to such a problem. Although, DNNs have not yet been introduced, it should have been sufficient to know that it is class of algorithms. However, brief glimpses of the main components of DNNs have been given under the image classification problem description.

The rest of the thesis will follow the following outline. \Cref{chp:dnn} introduces deep neural networks for image classifcation. Convolutional neural networks are specifically good at image classification and therefore most of the chapter will deal with them. The main focus is on the different structures and layers of the networks and how these influence performance (review this sentence - probably need to elaborate). 

\Cref{chp:mlc} starts with the fundamentals of multi-label classification. It includes a formal definition and emphasis on the important concepts, such as multi-label evaluation metrics and the modelling of label dependencies (maybe add class imbalance here). The chapter also includes a review of the state-of-the-art algorithms for MLC. A discussion is given on the challenges and ongoing research of the field. One of the objectives of this chapter is to find approaches that could help extend DNNs for multi-label image classification. 

\Cref{chp:dnn_mlc} reviews deep learning approaches for multi-label image classification. It looks at practically all of the proposals in the latest literature, how they attempt to model multiple labels and what are their shortcomings. The extensions are mostly adaptions of loss functions to be optimised or structural changes of the networks. An extensive comparision of the approaches is an important part of the chapter. Should I make proposals in this chapter?

\Cref{chp:results} evaluates the highlighted approaches in previous chapter on popular benchmark image datasets. Note that more on the benchmark datasets are given in \Cref{app:data}. The goal is to give a comprehensive empirical comparison of the best representative approaches in terms of many multi-label evaluation metrics (with standard errors). It includes discussions on the challenges of implementing these approaches and how the results correlate with the literature. The experiments done in this chapter are made as reproducible as possible with additional information on the code and software given in \Cref{app:code}.

The thesis is concluded in \Cref{chp:conc} with a summary of the work done in this project, general discussion of the literature and results and what directions can be followed for future research. It includes a section on the limitations of this study.